Meta RL analyses

### 2018-11-26 meta_RL_analyses.Rmd
Slightly better comparisons

```{r}
library(tidyverse)
library
```

```{r}
num_runs = 1
results_dir = "results/paper_results/"

result_subdirs = c("nometa")#, "nometa_su_heldout", "nometa_random_holdout",
                   #"basic", "basic_su_heldout", "basic_random_holdout")

@@

```{r}
ggplot(avg_sweep_d, aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ run_type)
```
# meta mapping (true) evaluation

```{r}
meta_d = load_d(results_dir, c("basic", "basic_su_heldout"), num_runs, "new_meta_true_losses")

>>>>

```{r}
library(tidyverse)
```

```{r}
num_runs = 7
results_dir = "results/paper_results/"

result_subdirs = c("nometa", "nometa_su_heldout", "nometa_random_holdout",
                   "basic", "basic_su_heldout", "basic_random_holdout")

@@

```{r}
ggplot(avg_sweep_d, aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ run_type)
```

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

# meta mapping (true) evaluation

```{r}
meta_d = load_d(results_dir, c("basic", "basic_su_heldout", "basic_random_holdout"), num_runs, "new_meta_true_losses")
